Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-20 manuscript.tex
commit before pulling
Edited EoR window figure and caption

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{plots/cosmicEvo.png}
	\caption{Rendering of cosmic evolution from just after the Big Bang to today (background image credit Loeb/{\em Scientific American}).  The blue line shows the frequency of the red-shifted hydrogen line (rest frequency 1420 MHz) as a function of redshift (lower horizontal axis) and cosmic time (upper horizontal axis).  The white dashed horizontal lines are the HERA EOR band and the blue are the extended frequency goal.  Determining where the structure in the background really falls is the
goal of HERA.} 
	\label{fig:cosmos}
\end{figure}

@@

\begin{figure}[t]
\centerline{
\includegraphics[height=3in]{plots/wedges.pdf}
}
\caption{The EoR ``window'' and foreground ``wedge'' are shown in this plot, which splits the wavenumber into $\kvpr$ (horizontal) and $\kpar$ (vertical) components.
Smooth-spectrum foregrounds with an intrinsic spectrum indicated by the gray bar along the bottom create the ``wedge'' when they interact with the interferometer's chromatic response, shown with a foreground image from the MWA.  Systematics can extend the wedge to the upper left.  The EoR window (shown with a simulation
from \citealt{mesinger_et_al2011}) to the upper left should be free from foregrounds.}
\label{fig:wedge}
\end{figure}

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{plots/cosmicEvo.pdf}
	\caption{Rendering of cosmic evolution from just after the Big Bang to today (background image credit Loeb/{\em Scientific American}).  The blue line shows the frequency of the red-shifted hydrogen line (rest frequency 1420 MHz) as a function of redshift (lower horizontal axis) and cosmic time (upper horizontal axis).  The white dashed horizontal lines are the HERA EOR band and the blue are the extended frequency goal.  %Determining where the structure in the background really falls is the goal of HERA.  
CMB observations observe the afterglow of the Big Bang (far left) and Baryonic Acoustic Oscillation (BAO) surveys proposed 
target $z\approx$0.8-2.5.  Limited surveys span back to about $z\approx$7.} 
	\label{fig:cosmos}
\end{figure}

@@

%\begin{figure}[t]
%\centerline{
%\includegraphics[height=3in]{plots/wedges.pdf}
%}
%\caption{The EoR ``window'' and foreground ``wedge'' are shown in this plot, which splits the wavenumber into $\kvpr$ (horizontal) and $\kpar$ (vertical) components.
%Smooth-spectrum foregrounds with an intrinsic spectrum indicated by the gray bar along the bottom create the ``wedge'' when they interact with the interferometer's chromatic response, shown with a foreground image from the MWA.  Systematics can extend the wedge to the upper left.  The EoR window (shown with a simulation
%from \citealt{mesinger_et_al2011}) to the upper left should be free from foregrounds.}
%\label{fig:wedge}
%\end{figure}

\begin{figure}[t]
	\centering
%	\vspace{-10pt}
	\includegraphics[width=1\textwidth,clip]{plots/Josh_Window_Data_Cartoon_v3.pdf}
	\vspace{-10pt}
	\caption{Foregrounds are a primary challenge facing 21\,cm cosmology experiments. 
HERA leverages a ``wedge'' in the cylindrically-averaged ($\mathbf{k}$ is broken into $k_\|$ and $k_\perp$) power spectrum (center panel). Smooth-spectrum foregrounds (right panel) $\sim$5 orders of magnitude brighter than fiducial EoR models (left panel; \citealt{mesinger_et_al2011}) create the ``wedge'' when they interact with the interferometer's chromatic response. Flat spectrum foregrounds cannot contaminate the EoR window beyond the horizon wedge, though intrinsic or imperfectly calibrated chromaticity can push it slightly beyond the horizon. By avoiding foregrounds, PAPER has placed limits within an order
of magnitude (in mK) of these models \citep{ali_et_al2015} and show the ``EoR Window'' to be foreground-free.
HERA's dish and compact configuration optimize wedge/window isolation and direct sensitivity to low-$k_\perp$ modes where the EoR is brightest relative to the foreground wedge.
}	\label{fig:wedge}
%\vspace{-10pt}
\end{figure}
